%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Backend Engineer} % Job title
{Blue Ocean Teach} % Organization
{Havana, Cuba} % Location
{Oct. 2017 - present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item {Backend services for a enterprise search solution}
  \item {Frameworks/languages: Play/Akka-HTTP/Scala}
  \item {Data store: ElasticSearch}
  \item {Microservices comunication layer: Kafka}
\end{cvitems}
}


%------------------------------------------------

\cventry
{Data Engineer} % Job title
{Blue Ocean Teach} % Organization
{Havana, Cuba} % Location
{Jul. 2017 - Sept. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item {ETL}
  \item {Frameworks/languages: Spark/Scala}
  \item {Data store: S3/Redshift}
\end{cvitems}
}


%------------------------------------------------

\cventry
{Backend Engineer} % Job title
{Blue Ocean Teach} % Organization
{Havana, Cuba} % Location
{Jan. 2017 - Jun. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
  \item {Backend services for a custom websearcher (Goghr/www.gogophr.com)}
  \item {Frameworks/languages: Play/Scala}
  \item {Data store: DynamoDb}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Project Manager} % Job title
{ALBET S.A.} % Organization
{Caracas, Venezuela.} % Location
{Jun. 2015 - Oct. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Integrating QFlow product (ACF Technologies) with the system of identity cards used in Venezuela}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Architect} % Job title
{Center of Internet Studies (University of Informatics Science)} % Organization
{La Havana, Cuba} % Location
{2009 - 2011} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Design and implementation of a system for managing queues at service offices}
\item {Leading a group of developers to implement a distributed system in Java}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
