%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Positions}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Backend Engineer} % Job title
{Freelancer} % Organization
{Havana, Cuba} % Location
{Jun. 2018 - present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Flask/Python}
\item {Google Speech-to-Text}
\item {Elasticsearch}
\item {Google App Engine Flexible}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Backend Engineer} % Job title
{Blue Ocean Teach} % Organization
{Havana, Cuba} % Location
{Jan. 2017 - Jun. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Play/Akka-HTTP}
\item {Scala/Java}
\item {DevOps: AWS, Docker}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Full-stack Web developer} % Job title
{Freelancer} % Organization
{Havana, Cuba} % Location
{Feb. 2016 - Dic. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Flask/Python}
\item {VueJS}
\item {Google App Engine Standard}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Researcher} % Job title
{Center of Computational Mathematics (University of Informatics Science)} % Organization
{Havana, Cuba} % Location
{Sep. 2014 - Feb. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Research about Parallel Evolutionary Algorithms}
\item {Implementation of Parallel Evolutionary Algorithms using Erlang}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Question/answering system consultor (Research Engineer)} % Job title
{Casabe} % Organization
{Havana, Cuba} % Location
{Jun. 2015 - Oct. 2015} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {State of the art analysis about Question/Answering systems}
\item {Organization of the development team}
\item {Development of POCs using: NLTK and Clojure}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Center of Internet Studies (University of Informatics Science)} % Organization
{Havana, Cuba} % Location
{Sep. 2004 - Jun. 2009} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {WebSearcher solution based on Lucene}
\item {Web Crawler implementation}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Internship} % Job title
{Center of Applied-Linguistic} % Organization
{Santiago de Cuba, Cuba} % Location
{Sep. 2000 - Jul. 2002} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Morphologic Analisis design and implementation}
\item {Implementation of a Lemmatization algorithm}
%\item {}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
